User Privacy in the Public Bitcoin Blockchain

### 2014-02-04 paper.tex
adds conclusion and related work

An example transaction is presented in listing~\ref{lst:bitcoin}.
Long hexadecimal strings have been trimmed to save space.
A transaction is identified by a hash, which is the first field.
This particular transaction has a single input (``in'') which is the first output (``n'':0) of a previous transaction with a hash starting with a777.

@@

>>>>

An example transaction is presented in Listing~\ref{lst:bitcoin}.
Long hexadecimal strings have been trimmed to save space.
A transaction is identified by a hash, which is the first field.
This particular transaction has a single input (``in'') which is the first output (``n'':0) of a previous transaction with a hash starting with a777.

@@

\section{Related Work}

The original paper proposing the Bitcoin network is \cite{nakamoto2008bpp}.
This paper already recommends avoiding address re-use and mentions the privacy threats associated to the use of change addresses.

An insightful analysis of the anonymity of the Bitcoin network is presented in \cite{reid2013aab}. 
Among other aspects, this paper covers the mechanisms to link public keys as belonging to the same user and how external information can be used to identify the users.
In some cases, the information publicly available on the Internet can be enough to identify users.
Centralized servers such as exchanges are in an even better position to de-anonymize the network.

A more recent work is \cite{meiklejohn2013fbc}, which describes in more detail the privacy attacks and the encountered difficulties in the process of de-anonymizing the Blockchain.
The authors actively participate in the Bitcoin ecosystem to be able to tag the most important services in the graphs derived from the Blockchain.
The Wikileaks case that we mention in our work is also considered in \cite{meiklejohn2013fbc}.

Both \cite{reid2013aab} and \cite{meiklejohn2013fbc} pay attention to bitcoin thefts and in some cases can track the money until a fraction of the theft reaches an exchange.

A simulation study on Bitcoin privacy \cite{androulaki2012eup} recommends the use of disposable addresses by the merchants for increased privacy protection.
The paper also mentions the collaborative construction of transactions and considers that its widespread use is unlikely.

\section{Conclusion}

The public availability of all Bitcoin transactions poses privacy-related challenges on the protocol.
In this work we discuss address re-use and CoinJoin transactions as two key privacy elements in Bitcoin.
The Bitcoin community is advancing in the understanding of privacy threats and developing mitigating techniques.
